A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-01-15 paper/draft.tex
additional info regarding party registration

Partisanship in Brazil is voluntary, with over 11 percent of registered voters affiliated to a party \citep{}

>>>>

Partisanship in Brazil is voluntary and widespread, with over 11 percent of registered voters affiliated to a party \citep{speck2015estudo}\footnote{For context, in most OECD countries party registration does not exceed 5 percent of the electorate. See \citet{biezen2014decline}.}. Registration occurs in the following sequence: a voter reports to a local party office, and the party officials then register the voter officially through the \emph{Tribunal Regional Eleitoral} (Regional Electoral Office). This registration is then centralized by the \emph{Tribunal Superior Eleitoral} (Supreme Electoral Office) and updated accordingly. If there are overlapping registrations, former ones become annulled and are reported as irregular to local party officials. Each voter is therefore only allowed to register for a single party, without any ceilings or floors regarding the duration of this affiliation.
